Variation in use of East Asian Late Paleolithic weapons: A study of tip cross-sectional area of stemmed points from Korea

### 2022-06-09 analysis/paper/paper.Rmd
added scatter plot for site&dates

 ggplot(tcsa_site_ass,
              # aes(reorder(min_tcsa, -age_ka), 
               aes(min_tcsa,
                  fill = n)) +
  geom_histogram() +
  theme_bw(base_size = 6) +
  labs(x = "TCSA", 
       y = "Count of artefacts") +
  facet_wrap(~label_site,
                 scales = "free_y",
                  ncol = 1) +
    scale_fill_viridis_c(name = "Number\nof artefacts")

>>>>

 # ggplot(tcsa_site_ass,
 #               aes(min_tcsa,
 #                  fill = n)) +
 #  geom_histogram() +
 #  theme_bw(base_size = 6) +
 #  labs(x = "TCSA", 
 #       y = "Count of artefacts") +
 #  facet_wrap(~label_site,
 #                 scales = "free_y",
 #                  ncol = 1) +
 #    scale_fill_viridis_c(name = "Number\nof artefacts")

 ggplot(tcsa_site_ass, aes(x = min_tcsa, y = reorder(label_site, age_ka), color = label_site)) +
   geom_point() +
   theme(legend.position="none") +
   labs(x = "TCSA", 
       y = "Assemblage")
